---
title: "Report Output 5 - Example"
output: html_document
---

```{r code block to load libaries and script, warning=FALSE, message=FALSE}
library('tidyverse')
library('DESeq2')
source('main.R')
```

# Load in counts matrix and sample metadata
```{r code block to load in subsetted data and subsetted sample data, message=FALSE}

```

# Display head of subsetted counts matrix
```{r code block to display head of subsetted counts matrix}

```

# Display subsetted coldata
```{r code block to display subsetted coldata}

```

# Run DESeq2 on subsetted counts matrix
```{r codeblock to run DESeq2 on subsetted data, message=FALSE}

```

```{r code block to define figure captions}
caption_1 <- 'Descriptive caption for fig 1'
caption_2 <- 'Descriptive caption for fig 2'
caption_3 <- 'Descriptive caption for fig 3'
caption_4 <- 'Descriptive caption for fig 4'
caption_5 <-  'Descriptive caption for fig 5'
```

# Plot of p-values for all results
```{r code block for p-values plot, fig.cap = caption_1}

```

# Plot of log2FC for differentially expressed genes
```{r code block for log2fc plot, fig.cap = caption_2}

```

# Volcano plot of results labeled by significance and directionality
```{r code block for volcano plot, fig.cap = caption_3}

```

# Extract out normalized counts for subsetted results
```{r code block to extract normalized counts and top ten DE genes ranked by padj}

```

# Plot normalized counts for top ten DE genes for subsetted results
```{r code block for normalized counts jitter plot, fig.cap = caption_4}

```

# Load in full counts matrix and sample data
```{r code block to read in full counts and full sampledata, message=FALSE}

```

# Run LRT analysis on full counts matrix
```{r codeblock for LRT analysis, message=FALSE}

```

# Plot normalized counts from LRT analysis for the top ranked DE gene across timepoints
```{r codeblock for normalized count plot for LRT, fig.cap=caption_5}

```